---
title: "Data Visualization (HW)"
author: "Kane.P"
date: "2022-11-02"
output:
  pdf_document: default
  word_document: default
---
# I.CO2 emission data set from kaggle
## Install packages and Import library
```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
```

## Data preparation
### 1.Import Data

```{r}
co2e <- read.csv("CO2_emission.csv")
co2e <- tibble(co2e)
wpop <- read.csv("world_population.csv")
wpop <- tibble(wpop)
```

### 2.Overview Data
```{r}
head(co2e,5)
```

### 3. transform from wide to long format
```{r}
co2_l <- co2e %>%
  select(1:3,5:34) %>%
  gather(X1990:X2019,
         key = "XYear",
         value = "MT_per_cap") %>%
  mutate(Year = as.character(str_extract_all(XYear,"\\d+")))
```

### 4. change data type
```{r}
co2_l <- co2_l %>%
  mutate(Year = year(as.Date(co2_l$Year,format = "%Y")))%>%
  select(-XYear)
head(co2_l,5)
```

### 5. Edit country name
```{r}
co2_l[co2_l == "Russian Federation"] <- "Russia"
co2_l[co2_l == "Iran, Islamic Rep."] <- "Iran"
co2_l[co2_l == "Venezuela, RB"] <- "Venezuela"
co2_l[co2_l == "Egypt, Arab Rep."] <- "Egypt"
co2_l[co2_l == "Yemen, Rep."] <- "Yemen"
co2_l[co2_l == "Syrian Arab Republic"] <- "Syria"
co2_l[co2_l == "Slovak Republic"] <- "Slovakia"
co2_l[co2_l == "Lao PDR"] <- "Laos"
co2_l[co2_l == "Korea, Rep."] <- "South Korea"
co2_l[co2_l == "Korea, Dem. People's Rep."] <- "North Korea"
```

## Data Visualization
### Chart1: CO2 emission metric tons per capita by country in 2019
```{r}
co2e_2019 <- co2_l %>%
  filter(Year == 2019)
```
```{r, fig.width=19,fig.height=11}
world_map <- map_data("world")
world_map[world_map == "USA"] <- "United States"
world_map[world_map == "Republic of Congo"] <- "Congo, Rep."
world_map[world_map == "Democratic Republic of the Congo"] <- "Congo, Dem. Rep."
world_map[world_map == "Turkey"] <- "Turkiye"
## Left join
co2e_map <- left_join(world_map, co2e_2019, by = c("region"="Country.Name"))
ggplot(co2e_map, aes(long, lat, group = group))+
  geom_polygon(aes(fill = MT_per_cap), color = "dark grey")+
  scale_fill_gradient(low = "light yellow", high = "red", na.value = NA)+
  theme_minimal()+
  theme(axis.text = element_text(size = 30),axis.title = element_text(size = 40),
        plot.title= element_text(size = 45),legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),plot.caption = element_text(size = 25))+
  labs(title = "CO2 emission metric tons per capita by country in 2019",
       x = NULL, y = NULL,
       caption = "Source: CO2 Emissions Around the World from kaggle")
```

### Chart2: CO2 emission metric tons by country in 2019
```{r, fig.width=19,fig.height=11}
wpop2020 <- wpop %>%
  select(2,3,5,7)
pop_map <- left_join(co2e_2019,wpop2020, by = c("country_code"="CCA3"))
pop_map <- pop_map %>%
  mutate(total_co2 = (MT_per_cap*X2020.Population*1000)/(10**6))
#leftjoin
pop_map <- left_join(pop_map, world_map, by = c("Country.Name"="region"))
#Visualization
ggplot(pop_map, aes(long, lat, group = group))+
  geom_polygon(aes(fill = total_co2), color = "dark grey")+
  scale_fill_viridis_c(option = "C", na.value = NA)+
  theme_minimal()+
  theme(axis.text = element_text(size = 30),axis.title = element_text(size = 40),
        plot.title= element_text(size = 45),legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),plot.caption = element_text(size = 25))+
  labs(title = "CO2 emission (metric tons) by country in 2019",
       x = NULL, y = NULL,
        caption = "Source: CO2 Emissions Around the World from kaggle
       (https://www.kaggle.com/datasets/koustavghosh149/co2-emission-around-the-world)")
```

### Chart3: Top 10 Most Polluting Countries Per Capita in 2019
```{r, fig.width=19,fig.height=11}
co2_l %>%
  filter(Year == 2019) %>%
  arrange(desc(MT_per_cap)) %>%
  head(10) %>%
  ggplot(aes(reorder(Country.Name , -MT_per_cap),MT_per_cap , fill = MT_per_cap))+
  geom_col()+
  geom_text(aes(label=round(MT_per_cap,digits = 2),
              vjust = 2))+
  scale_fill_gradient(low = "light yellow", high = "red", na.value = NA)+
  theme_minimal()+
  theme(axis.text = element_text(size = 20),axis.title = element_text(size = 40),
        plot.title= element_text(size = 45),legend.text = element_text(size = 15),
        legend.title = element_text(size = 25),plot.caption = element_text(size = 25))+
  labs(title = "Top 10 countries with the most polluters in 2019",
       x = "Country", y = "Co2 emissions (metric tons per capita)",
       caption = "Source: CO2 Emissions Around the World from kaggle")
```

### Chart4: Top 5 Most Polluting Countries by year
```{r,fig.width=19,fig.height=11}
TOP5 <- c("QAT","KWT","BHR","ARE","BRN")
co2_l %>%
  filter(country_code %in% TOP5) %>%
  ggplot(aes(Year,MT_per_cap, col = Country.Name))+
           geom_line(size = 2)+
  theme_minimal()+
  theme(axis.text = element_text(size = 30),axis.title = element_text(size = 40),
        plot.title= element_text(size = 45),legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),plot.caption = element_text(size = 25))+
  labs(title = "Co2 emission by Year",
       x = "Year", y = "Co2 emissions (metric tons per capita)",
       caption = "Source: CO2 Emissions Around the World from kaggle
       (https://www.kaggle.com/datasets/koustavghosh149/co2-emission-around-the-world)")

```

# II.Diamonds dataset from R
## Data preparation
### 1.Overview Data
```{r}
glimpse(diamonds)
```
### Data Description
+ carat	  : weight of the diamond
+ cut     : quality of the cut
+ color   :	diamond color
+ clarity :	measurement of how clear the diamond is
+ depth	  : total depth percentage
+ table	  : width of top of diamond relative to widest point
+ price	  : price in US dollars
+ x       :	length in mm
+ y	      : width in mm
+ z	      : depth in mm

### 2.Check Missing Values
```{r}
diamonds %>%
  is.na() %>%
  sum()
```
There is not missing values in diamonds data set.

### 3.data sampling
We sampled 10% of diamonds data set 
```{r}
set.seed(11)
diamonds_sampling <- diamonds %>%
  sample_n(5394)
```

## Data Visualization
### Chart01: The relationship between carat and price

```{r}
diamonds_sampling %>%
  ggplot(aes(carat,price,color= color))+
  geom_point(alpha = 0.5)+
  facet_wrap(~color, ncol = 4)+
  theme_minimal()+
  scale_color_brewer(type = "qual", palette = "YlGn")+
  labs(title = "Scatter plot of diamond Carat and Price(USD)",
       x = "Carat", y = "Price(USD)",
       caption = "Source: Diamond dataset in r")
```
This scatter plot shows a positive correlation between carat and price.The higher the carat, the higher the price.

### Chart02: Line chart between Clarity and Average Price
```{r}
diamonds_sampling %>%
  group_by(clarity,cut) %>%
  summarise(avg_price = mean(price)) %>%
  ggplot(aes(clarity, avg_price,group = cut, col = cut))+
  geom_point()+
  geom_line()+
  theme_minimal()+
  scale_color_brewer(type = "qual", palette = "YlGn")+
  labs(title = "Line chart of diamond Clarity and Average Price(USD)",
       x = "Clarity", y = "Avg_Price(USD)",
       caption = "Source: Diamond dataset in r")
  
```